Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
xxx

The benefits of MDSD have consistently been reported in academia . Many large companies such as Ericsson, Volvo and ABB also use MDSD as a part of their development chain. In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.

\SubSection{Statement of the Problem}
The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed. Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability. Since there seems to be a consensus in academia that MDSD is the future, and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.

@@

\SubSection{Research Questions}
\begin{itemize}
\item \textbf{RQ1:} In which situations should companies expect that changing to MDSD would lead to positive effects? 
\item \textbf{RQ1.1:} In which domain(s) is MDSD the most successful? 
\item \textbf{RQ1.2:} Which software development process(es) has been most successfully used in conjunction with MDSD?
\item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
\end{itemize}

>>>>

The benefits of MDSD have consistently been reported in academia \cite{staron2006adopting} \cite{volter2013model}. Many large companies such as Ericsson and ABB \cite{staron2006adopting} also use MDSD as a part of their development chain. In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.

\SubSection{Statement of the Problem}
The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed. Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability. Since there seems to be a consensus in academia that MDSD is an improvement compared traditional software development \cite{staron2006adopting} \cite{volter2013model} and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.

@@

\SubSection{Research Questions}
\begin{itemize}
\item \textbf{RQ1:} In which situations should companies expect that changing to MDSD would lead to positive effects? 
\item \textbf{RQ1.1:} In which domain(s) is MDSD the most successful? 
\item \textbf{RQ1.2:} Which software development process(es) has been most successfully used in conjunction with MDSD?
\item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
\item \textbf{RQ1.4:} Which change strategy has most successful in implementing MDSD? 
\end{itemize}
